---
title: "Advent of Code"
description: |
  A new article created using the Distill format.
author:
  - name: Julian During
    url: www.datannery.com
date: "`r Sys.Date()`"
output: distill::distill_article
params:
  interactive: TRUE
editor_options: 
  chunk_output_type: console
repository_url: https://github.com/duju211/advent_of_code
base_url: https://www.datannery.com/posts/advent_of_code/
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source(here::here("setup.R"))
```

# Idea

Advent of code is a annual coding competition. In the following I want to
briefly discuss my solutions and hopefully get as far as possible :-).

The following libraries are used to solve the challenges:

```{r, eval=FALSE}
library(tidyverse)
```


## Day 1

In part one we are told to get the first and last digit from a string.
Combine these and add them together.

```{r, file=here::here("R", "trebuchet.R")}
```

For the 'training' data this looks like this:

```{r, echo=FALSE}
tar_read(df_trebuchet_train)
```

For the second part, numbers can also be represented as words. The code
for this solution looks like this:

```{r, file="R/trebuchet_2.R"}
```

For the training data the result looks like this:

```{r, echo=FALSE}
tar_read(df_trebuchet_2_train)
```